---
title: "R for HMIS Admins"
author: "Genelle Denzin"
date: "6/30/2020"
output: 
  ioslides_presentation:
    logo: COHHIOlogo_5.16.jpg
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

# Week 4: Tidyverse

Presenter: Genelle Denzin (she/her)
(HMIS Data Analyst, a co-organizer of Columbus R-Ladies)

Co-presenter: Carolyn Hoffman (fellow R user, Training & Technical Assistance)

## Homework

Feedback on the homework? Any trouble installing the Tidyverse? Questions about the HUD CSV Export? How was the tutorial?

## Logistics

- Access to two monitors will be ideal.

- Please send questions/comments to the chat or raise your hand if you need to ask a question and I can unmute you. 

- Check the readme at the GitHub link for resources, links to recordings, homework instructions, etc. Contact me directly if you have any questions.

### https://github.com/kiadso/rTraining

## What is the Tidyverse?

A set of R packages created and maintained by RStudio which adheres to the concept of "tidy" data.

Intended to make coding in R more accessible to "non-coders".

Because the packages are bundled and maintained together, it makes it much easier to know the packages you are using will work well together. (Not always a given!)

## What Packages are in the Tidyverse?

Most commonly used within the [Tidyverse](https://www.tidyverse.org/packages/): 

- lubridate
- dplyr
- ggplot2
- readr
- stringr

I generally call:

```{r pkgs, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(lubridate)
```

## Demo Preview

* Using your own HUD CSV Export, we will use R Markdown to create a one-off report
* Objective: create a dataframe that lists each Organization Name along with how many HMIS-participating providers are associated with that Organization.

# Demo

## Homework 

- Nothing specific! Play around with your HMIS data, bring something to show/share in Week 5!

## IF YOU ARE SO INCLINED

- Donations to COHHIO's Pandemic Fund which helps organizations in Ohio keep our homeless neighbors safe from COVID-19. https://actionnetwork.org/fundraising/cohhio-pandemic-emergency-fund

- Donations to the Columbus Freedom Fund which bails out local Black Lives Matter protesters can be made here: https://www.paypal.me/columbusfreedomfund

# Turning You Loose!

Last Session Topic:
